LAGOS lake depth

### 2020-11-24 figures/01_geometry.Rmd
cleanup fig2b alternatives, #22

gg_slope_alternative <- function(nearshore_var, inlake_var, dt){
  # dt <- test
  # nearshore_var <- "nearshore_slope_mean"
  # inlake_var <- "inlake_slope_pnt"
  rsq <- round(broom::glance(
    lm(as.formula(paste0(nearshore_var, " ~ ", inlake_var)), data = dt)
    )$r.squared, 2)
  res <-  ggplot(data = dt) + 
    geom_point(aes(.data[[nearshore_var]], .data[[inlake_var]]), size = 1) +
    geom_smooth(aes(.data[[nearshore_var]], .data[[inlake_var]]), 
                method = "lm", se = FALSE) +
    geom_rect(xmin = 0.28, xmax = 0.42, ymin = 0, ymax = 0.05,
    alpha = 1, fill = "white") +
    annotate("text", x = 0.34, y = 0.05, label = paste0("R^2 == ", rsq),
                                  parse = TRUE, size = text_size-0.7) +
    # annotate("label", x = 0.27, y = 0.01, 
    #          label = get_formula(
    #            lm(inlake_slope_pnt ~ nearshore_slope_mean, data = test)), 
    #          size = text_size-0.85, fill = "white", label.size = NA) +
    # geom_abline(slope = 1, intercept = 0) +
    xlab(nearshore_var) +
    ylab(inlake_var) +
    labs(color = "") +
    theme_opts

@@

@@

@@

cowplot::plot_grid(plotlist = gg_slope_list, 
                   nrow = 5, byrow = FALSE, 
                   rel_heights = c(rep(0.6, 4), 1,
                                   rep(0.6, 4), 1,
                                   rep(0.6, 4), 1))
```

>>>>

gg_slope_alternative <- function(nearshore_var, inlake_var, dt){
  # dt <- test
  # nearshore_var <- "nearshore_slope_mean"
  # inlake_var <- "inlake_slope_pnt"
  rsq <- round(broom::glance(
    lm(as.formula(paste0(nearshore_var, " ~ ", inlake_var)), data = dt)
    )$r.squared, 2)
  res <-  ggplot(data = dt) + 
    geom_point(aes(.data[[nearshore_var]], .data[[inlake_var]]), size = 1) +
    geom_smooth(aes(.data[[nearshore_var]], .data[[inlake_var]]), 
                method = "lm", se = FALSE) +
    # geom_rect(xmin = 0.28, xmax = 0.42, ymin = 0, ymax = 0.05,
    # alpha = 1, fill = "white") +
    annotate("label", x = 0.4, y = 0.52, label = paste0("R^2 == ", rsq),
                                  parse = TRUE, size = text_size-0.7) +
    # annotate("label", x = 0.27, y = 0.01, 
    #          label = get_formula(
    #            lm(inlake_slope_pnt ~ nearshore_slope_mean, data = test)), 
    #          size = text_size-0.85, fill = "white", label.size = NA) +
    # geom_abline(slope = 1, intercept = 0) +
    xlab(stringr::str_replace_all(nearshore_var, c("nearshore_" = "", "_mean" = ""))) +
    ylab(pad_str(stringr::str_replace_all(inlake_var, c("inlake_" = "")), 
                 18)) +
    xlim(c(0, 0.6)) + ylim(0, 0.6) +
    labs(color = "") +
    theme_opts +
    theme(axis.title = element_text(family = "mono"))

@@

# pad_str(
#   stringr::str_replace_all(
#     slope_alternatives$inlake_slope, c("inlake_" = "")),
#   18)

@@

gg_slope_list[c(1:5)] <- lapply(
  gg_slope_list[c(1:5)], function(x) x +
     theme(
       # axis.title.y = element_blank(), 
       axis.title.y = element_text(angle = 0)))

@@

xlab <- ggdraw() + draw_label("nearshore")
ylab <- ggdraw() + draw_label("inlake", angle = 90)
cowplot::plot_grid(
  ylab,
cowplot::plot_grid(
cowplot::plot_grid(plotlist = gg_slope_list, 
                   nrow = 5, byrow = FALSE, 
                   rel_heights = c(rep(0.6, 4), 1),
                   rel_widths = c(rep(1, 1), 
                                  rep(0.37, 2))), 
xlab, ncol = 1, rel_heights = c(1, 0.1)), 
ncol = 2, rel_widths = c(0.1, 1))
```
